Visually pleasing knot projections

### 2021-09-26 inst/jma_knot.tex
fixes #36

Consider Figure~\ref{knot_table} from an \ae sthetic perspective; the
diagrams are representative of those available under a free license.
However, these diagrams are not suitable for high-quality artwork such
as posters: they are not vectorized.  Many of the underlying knots
possess a line of symmetry (at least, the diagrams do if the breaks
are ignored), which is not present in the visual representation.
Also, several of the strands cross at acute angles.  The diagram for
knot~$7_3$, for example, contains ugly kinks and abrupt changes of
curvature.

@@

The knot shown in Figure~\ref{screenshot_inkscape_7_6} is clearly
suboptimal: even though the nodes are connected by Bezier curves which
are individually smooth, the path as a whole is ugly and unattractive
as its path has unsightly regions where the radius of curvature
changes abruptly.

@@

(the above takes about an hour of CPU time: it is optimizing a
function of~64 real variables, and the objective function takes a few
seconds to evaluate).  However, the result is much nicer
(Figure~\ref{7_6}).

>>>>

Consider Figure~\ref{knot_table} from an \ae sthetic perspective; the
diagrams are representative of those available under a free license.
However, these diagrams are not suitable for high-quality artwork such
as posters: they are not vectorized.  Many of the underlying knots
possess a line of symmetry (at least, the diagrams do if the breaks
are ignored), which is not present in the visual representation.
Also, several of the strands cross at acute angles.  The diagram for
knot~$7_3$, for example, contains kinks and abrupt changes of
curvature which distract from the underlying topological form.

@@

The knot shown in Figure~\ref{screenshot_inkscape_7_6} is clearly
suboptimal: even though the nodes are connected by Bezier curves which
are individually smooth, the path as a whole is visually disjointed as
it has places where the radius of curvature changes abruptly.

@@

(the above takes about an hour of CPU time: it is optimizing a
function of~64 real variables, and the objective function takes a few
seconds to evaluate).  However, the result is visually smoother and
thus arguably more attractive (Figure~\ref{7_6}).
